%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limitx
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sicong}{Jiang}{ \urlstyle{same} 
\href{mailto:kevin.jiangsc@gmail.com}{kevin.jiangsc@gmail.com} | (608)609-3496
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Wisconsin}
\descript{BS in Computer Science}
\location{May 2016 | Madison, WI\\
Cum. GPA: 3.19}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Over 1000 lines:}
Java \textbullet{} Matlab \textbullet{} C \textbullet{} Python \textbullet{} JavaScript\\ 
\location{Familiar:}
Scheme \textbullet{} Swift \textbullet{} SQLite 	\\
Assembly Language(x86)\textbullet{}\LaTeX\
\sectionsep

\subsection{Web Development Skills}
JavaScript\textbullet{}JSF\textbullet{}Spring\textbullet{}JSP\\
Struts\textbullet{}BootStrap\textbullet{}WebGL\textbullet{}Hibernate
\sectionsep

\subsection{Database Skills}
SQLite \textbullet{}PostgreSQL\textbullet{}OracleSQL
\sectionsep

\subsection{Tools}
Git \textbullet{} SubVersion  \textbullet{} Vim \\
Eclipse \textbullet{} Xcode \textbullet{} Maven
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Algorithm			\\
Artificial Intelligence  \\
Computer Organization	\\
Computer Graphics	\\
Computer Networks	\\
Computational Photography \\
Human-Computer Interaction \\
Mobile System and Application \\
Operating Systems \\
Unix Tools and Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/kevinsj}{\bf KevinSJ} \\
LinkedIn://  \href{https://www.linkedin.com/in/kevsj}{\bf Kevin Jiang} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.67\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{\href{http://www.topslab.wisc.edu/}{Traffic Operations And Safety Lab}}
\descript{| Research Intern }
\location{Nov 2014 – Current | Madison, WI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked in primarilly Java using Struts framework to maintain and develop new functionality for the Wisconsin Lane Closure System
\item Adding pagination to the search results and integrate Google Map to the WisLCS system using Javascript API to make it easy for users to select landmarks. In production.
\item Continue as a research intern after graduation to develop various enhancements for Wisconsin Transportation Management System using Spring, Hibernate and JavaServer Faces. Currently focus on developing section-based comment for the system.
\item Using Spring, Hibernate and Datatable to develop 511 Travel Times which is used to retrive travel times data in Wisconsin from archive.
\end{tightemize}
\sectionsep

\runsubsection{ALSTOM HIGH VOLTAGE SWITCHGEAR CO.}
\descript{| IT Helpdesk Intern}
\location{May 2014 – August 2014 | Suzhou, Jiangsu, China}
\begin{tightemize}
\item Ensure proper recording, documentation and closure with troubleshotting calls.
\item Troubleshoot and resolve basic network and server access problems for end-users from the Help Desk. 
\item Migrate client workstations from Windows XP to Windows 7.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Course Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Academic Projects}

\runsubsection{Tutor Finder}
\descript{}
\location{Feb 2016 - May 2016 }
Worked in group to design and develop a iOS tutor finding app using Swift. The tutor finder app is intended to use as a tool for college students help each other, they can choose to be either a tutor or tutee to help each other. The app is developed using Loopback framework.
\sectionsep

\runsubsection{\lc{http://go.wisc.edu/ul9c0x}{Image Dehazing using Dark Channel Prior}}
\descript{}
\location{Mar 2015  - May 2015 }
Worked with partner to develop and compare different dark channel prior algorithm that can be used to solve the problem of hazy images. All algorithms were implemented using MATLAB.
\sectionsep

\runsubsection{Simple Unix Shell}
\descript{}
\location{Sep 2015 - Dec 2015 }
A simple shell implemented in C with support for Batch and Interactive modes, command history and redirection.
\sectionsep

\runsubsection{XV6 Kernel Hack}
\descript{}
\location{Sep 2015 - Dec 2015 }
Implemented MLFQ scheduler, threading support, dynamic stack growth functionality and a reliable file system in C.
\sectionsep

\iffalse
\runsubsection{Redesign Yahoo Finance}
\descript{}
\location{Mar 2014  - May 2014 }
Worked in a group to resigned the Yahoo Finance app and include the function of adding favorite stock.
\sectionsep
\fi

\iftrue
\section{Side Projects}

\runsubsection{\href{http://www.projectjtw.xyz/}{Project Journey to the West}}
\descript{}
\location{Apr 2016 - Current}
Project Journey to the West is designed to use modern web technologies to introduce the classic Chinese novel \textit{Journey to the West} to readers whose native language is not Chinese. The project is built using Node.js, D3.js and Bootstrap.  
\sectionsep
\fi


\end{minipage} 
\end{document}  \documentclass[]{article}